### 2020-03-08 appendix.tex
update
I'm going to stop fiddling...

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap_03.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0_03.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 
We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.3$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap_08.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0_08.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are wide. 
We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.8$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap_kappa.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_kappa_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the generation-interval dispersion of asymptomatic cases.
(A) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
(B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
We vary $\kappa_a/\kappa_s$ while assuming $1/r=7$ days, $\bar G_s=\bar G_a=8$ days, and $\kappa_s=0.5$.
The solid, white lines represent the contours.
}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap_03.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0_03.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.3$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap_08.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0_08.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are wide. 
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.8$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap_kappa.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_kappa_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the generation-interval dispersion of asymptomatic cases.
(A) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
(B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
The white, solid lines represent the contour lines.
Here, we assume $1/r=7$ days, $\bar G_s=\bar G_a=8$ days, and $\kappa_s=0.5$.
}
\end{center}
\end{figure*}

### 2020-03-08 short.body.tex
I'm going to stop fiddling...

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases. 
(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
The white lines represent the contours.
The white circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
\label{fig.relevance}}
\end{center}
\end{figure*}

@@

As an example, we assume that 18\% of the newly infected cases are asymptomatic \citep{mizumoto_2020} and that the asymptomatic cases are as half as infectious as the symptomatic ones (i.e., $\mathcal R_a = 0.5 \mathcal R_s$).
The intrinsic proportion of asymptomatic transmission $z$ is 0.11, whereas asymptomatic cases can account for anywhere between 6\% and 16\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore (Figure~\ref{fig.relevance}A).
Likewise, the basic reproduction number ranges between 2.3 and 2.6 (Figure~\ref{fig.relevance}B).
Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; red circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.

>>>>

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases. 
(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
Depending on whether $G_a$ is smaller (left side of the white, dashed line) or bigger (right side of the white, dashed line) than $G_s$, naive estimate that does not explicitly account for asymptomatic transmission over- or under-estimates the true $\mathcal R_0$.
The white circles represent the baseline value at $p=0.18$ and $\mathcal R_a = 0.5 \mathcal R_s$.
The white, solid lines represent the contour lines.
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
\label{fig.relevance}}
\end{center}
\end{figure*}

@@

As an example, we assume that 18\% of the newly infected cases are asymptomatic \citep{mizumoto_2020} and that the asymptomatic cases are as half as infectious as the symptomatic ones (i.e., $\mathcal R_a = 0.5 \mathcal R_s$).
The intrinsic proportion of asymptomatic transmission $z$ is 0.11 (white circle in Figure~\ref{fig.relevance}A), but asymptomatic cases can account for anywhere between 6\% and 16\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore.
Likewise, the basic reproduction number ranges between 2.3 and 2.6.
Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; white circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
